---
title: "Reproducible Research Peer Assessment"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for Loading/Reading the data

```{r}
myfile <- read.csv(unz("activity.zip", "activity.csv"),header=T,)
summary(myfile)
```

## Code for Preprocessing the data
### Remove Missing values (NA)
```{r}
x <- as.data.frame(myfile[complete.cases(myfile), ])
summary(x)
head(x)
```

## Histogram of the total number of steps taken each day
```{r}
require(magrittr)
require(dplyr)
steps_sum<- x %>% group_by(date) %>% summarize(Total_Steps=sum(steps))
str(steps_sum)
hist(steps_sum$Total_Steps)
```

## What is mean total number of steps taken per day?
## Mean and median number of steps taken each day
```{r}
steps_tally<-summary(steps_sum)
str(steps_tally)
paste(steps_tally[3,2],steps_tally[4,2],sep='    ')
```

## What is the average daily activity pattern?
## Time series plot of the average number of steps taken
```{r, fig.height=7}
require(magrittr)
require(dplyr)
require(plotly)
require(lubridate)
steps_mean <- x %>% group_by(date) %>% summarize(mean_Steps=mean(steps))
str(steps_mean)
plot(steps_mean$mean_Steps~as.factor(substr(as.character(steps_mean$date),6,10)), type="p", xlab="Month-Date", ylab="Daily Average Steps")
lines(steps_mean$mean_Steps)
plot_ly(x = ~substr(as.character(steps_mean$date),6,10), y = ~steps_mean$mean_Steps, mode = 'lines', height=5, xlab="Month-Date", ylab="Daily Average Steps")

ts(steps_mean)
hist(steps_sum$Total_Steps)
steps_tally<-summary(steps_sum)
str(steps_tally)
paste(steps_tally[3,2],steps_tally[4,2],sep='    ')
```

The 5-minute interval that, on average, contains the maximum number of steps
Histogram of the total number of steps taken each day after missing values are imputed
Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

All of the R code needed to reproduce the results (numbers, plots, etc.) in the report






Code to describe and show a strategy for imputing missing data
## Imputing missing values


```{r pressure}

```
