---
title: "Reproducible Research Peer Assessment"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading/Reading the data

Note that the variable to track the number steps has 2304 missing entries 'NA'.

```{r}
myfile <- read.csv(unz("activity.zip", "activity.csv"),header=T,)
summary(myfile)
```

### Preprocessing the data - Remove Missing values (NA)

1. Use the variable date to determine if it is a weekday or weekend.
2. Classify day of the week into two groups: weekday and weekend
3. Define a subset of records without any missing values.

```{r}
myfile$day <- weekdays(as.Date(myfile$date))
unique(myfile$day)
is_weekend <- myfile$day %in% c("Saturday","Sunday")
myfile$day_type <- "weekday"
myfile[is_weekend,]$day_type <- "weekend"
unique(myfile$day_type)
x <- as.data.frame(myfile[complete.cases(myfile), ])
summary(x)
```

### Plot Histogram of the total number of steps taken each day
```{r}
require(dplyr)
daily_steps_sum<- x %>% group_by(as.factor(date)) %>% summarize(Total_Steps=sum(steps))
hist(daily_steps_sum$Total_Steps,main = "Histogram of total number of steps taken per day", xlab = "Total number of steps", ylim=c(0,30))
```

### Find Mean and median number of steps taken per day
```{r}
steps_tally<-summary(daily_steps_sum)
paste(steps_tally[3,2],steps_tally[4,2],sep='    ')
```

### Time series plot of average daily activity pattern in terms of average number of steps taken
```{r}
require(dplyr)
steps_mean_interval <- x %>% group_by(interval) %>% summarize(mean_steps_interval=mean(steps))
str(steps_mean_interval)
plot(y=steps_mean_interval$mean_steps_interval,x=steps_mean_interval$interval, type="l", xlab="5-minute Interval", ylab="Interval Average Steps", main="average daily activity pattern")
```

### Find the 5-minute interval that, on average, contains the maximum number of steps

1. Find the index where the maximum average number of step is.
2. Find the 5-minute interval with the found index.

```{r}
index <-which.max(steps_mean_interval$mean_steps_interval)
steps_mean_interval$interval[index]
```

### Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

It can seen that people were walking more over the weekends.

```{r, echo=TRUE, fig.height=7}
require(dplyr)
steps_mean_wkday <- x %>% group_by(day_type, interval) %>% summarize(mean_Steps_day=mean(steps))
str(steps_mean_wkday)
par(mfrow=c(2,1))
lapply(unique(x$day_type), function(wkday) {
  wkday_data <- steps_mean_wkday[which(steps_mean_wkday$day_type==wkday),]
  wkday_p<-plot(wkday_data$mean_Steps_day ~ wkday_data$interval, xlab=wkday,
    ylab="avg steps per 5-min interval", type="l")
  wkday_p
  }
)
```

### Srategy and codes for imputing missing values

1. The variable steps has total 2304 missing values in the dataset, i.e. the total number of rows with NAs.
```{r}
is_missing <- is.na(myfile$steps)
table(is_missing)
```
2. The strategy is to use the mean of each 5-minute interval for either weekend or weekday to fill in all of the missing values for steps variable in the dataset.

```{r}
library(dplyr)
myfile$steps_imp <- myfile$steps 
myfile <- left_join(myfile, steps_mean_wkday, by = c("day_type","interval"))
myfile <- transform(myfile, steps_imp=ifelse(is.na(steps), mean_Steps_day, steps))
head(myfile)
```

### Histogram of the total number of steps taken each day after missing values are imputed
```{r}
require(dplyr)
steps_imp_sum<- myfile %>% group_by(as.factor(date)) %>% summarize(Total_Steps=sum(steps_imp))
str(steps_imp_sum)
hist(steps_imp_sum$Total_Steps,main = "Histogram of total number of steps with imputation taken per day", xlab = "Total number of steps imputed", ylim=c(0,40))
```
